---
title: "gpelose_OrigianlHomework_week3"
author: "Greg Pelose"
date: "9/16/2019"
output: html_document
---

Homework Question:
Every Saturday, at the same time, a primatologist goes and sits in the forest in the morning and listens for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

1. What is the probability that she will hear more than 8 calls during any given session?

```{r}
ppois(8, lambda=15, lower=FALSE)
```

2. What is the probability that she will hear no calls in a session?

```{r}
dpois(0, lambda=15)
```

3. What is the probability that she will hear exacty three calls in a session?

```{r}
dpois(3, lambda=15)
```

4. Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.

```{r}
x <- 0:30
dpois(x=x, lambda=15)
data <- dpois(x=x, lambda=15)
barplot(data, names.arg = x, space = 0, xlab="calls", ylab="probability", main = "Probability of Calls")
```

5. Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions)

```{r}
rpois(104, lambda = 15)
```

6. Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?

```{r}
x <- rpois(104, lambda = 15)
hist(x, xlim= range(0:30), xlab="calls", main="Frequency of Calls")
```




